Relative Stable Maps in Genus One via Central Alignments

### 2018-03-22 genus-one-relative-maps.tex
Minor changes

  \begin{remark}
   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any deformation as a log smooth curve will automatically be minimal centrally aligned. The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.
  \end{remark}

>>>>

  \begin{remark}
   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any first-order deformation as a log smooth curve will automatically be minimal centrally aligned. The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.
  \end{remark}
